Why is Stochastic Lambda > Deterministic?

### 2022-04-26 notes/understanding stochastic lambda.Rmd
updated notes

-   Get code to run

@@

-   add analysis with CF

-   Don't normalize population sizes and plot both CF and FF as PVA for both models

-   Try year as fixed effect

@@

```{r}
all_lams <-
  list(ff = ipm_stoch_ff, cf = ipm_stoch_cf) %>% 
  map_df(
    ~tibble(year = .x$env_seq,
         lambda = lambda(.x, type_lambda = "all")[,1])%>% 
  #remove burnin
  slice(101:n()),
  .id = "habitat"
  )

@@

```{r lambdas}
tribble(~model, ~habitat, ~year, ~lambda,
        "det", "ff", "both combined", lambda(ipm_det_ff),
        "stoch", "ff", "both combined", lambda(ipm_stoch_ff, log = FALSE),
        "det", "cf", "both combined", lambda(ipm_det_cf),
        "stoch", "cf", "both combined", lambda(ipm_stoch_ff, log = FALSE),
        "det", "ff", "2001", lambdas_ff[2],
        "det", "ff", "2003", lambdas_ff[4],
        "det", "cf", "2001", lambdas_cf[2],
        "det", "cf", "2003", lambdas_cf[4]
) %>% 
  bind_rows(
    all_lams %>%
      group_by(habitat, year) %>%
      summarize(lambda = mean(lambda)) %>% 
      mutate(year = paste(year, "mean"),
             model = "stoch")
  ) %>% arrange(model, habitat)
```

>>>>

@@

-   Plot population trajectories for all models

@@

```{r class.source = 'fold-hide'}
all_lams <-
  list(ff = ipm_stoch_ff, cf = ipm_stoch_cf) %>% 
  map_df(
    ~tibble(year = .x$env_seq,
         lambda = lambda(.x, type_lambda = "all")[,1])%>% 
  #remove burnin
  slice(101:n()),
  .id = "habitat"
  )

@@

```{r lambdas, class.source = 'fold-hide'}
tribble(~model, ~habitat, ~year, ~lambda,
        "det", "ff", "both combined", lambda(ipm_det_ff),
        "stoch", "ff", "both combined", lambda(ipm_stoch_ff, log = FALSE),
        "det", "cf", "both combined", lambda(ipm_det_cf),
        "stoch", "cf", "both combined", lambda(ipm_stoch_ff, log = FALSE),
        "det", "ff", "2001", lambdas_ff[2],
        "det", "ff", "2003", lambdas_ff[4],
        "det", "cf", "2001", lambdas_cf[2],
        "det", "cf", "2003", lambdas_cf[4]
) %>% 
  bind_rows(
    all_lams %>%
      group_by(habitat, year) %>%
      summarize(lambda = mean(lambda)) %>% 
      mutate(year = paste(year, "mean"),
             model = "stoch")
  ) %>% arrange(model, habitat)
```
